Comparing and combining network-guided biomarker discovery to discover genetic susceptibility mechanisms to breast cancer on the GENESIS study

### 2021-02-25 manuscript/plos/review_3.tex
added final (?) review

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Boosting GWAS using biological networks: a study on susceptibility to familial breast cancer} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Héctor Climente-González\textsuperscript{1,2,3,4*}, 
Christine Lonjou\textsuperscript{1,2,3}, 
Fabienne Lesueur\textsuperscript{1,2,3},
GENESIS study group\textsuperscript{\textpilcrow},
Dominique Stoppa-Lyonnet\textsuperscript{5,6,7\textcurrency}, 
Nadine Andrieu\textsuperscript{1,2,3}, 
Chloé-Agathe Azencott\textsuperscript{3,1,2}
\\
\bigskip
\textbf{1} Institut Curie, PSL Research University, F-75005 Paris, France;\\
\textbf{2} INSERM, U900, F-75005 Paris, France;\\
\textbf{3} MINES ParisTech, PSL Research University, CBIO-Centre for Computational Biology, F-75006 Paris, France;\\
\textbf{4} RIKEN Center for Advanced Intelligence Project (AIP), Tokyo, Japan; \\
\textbf{5} Service de Génétique, Institut Curie, F-75005 Paris, France;\\
\textbf{6} INSERM, U830, F-75005 Paris, France;\\
\textbf{7} Université Paris Descartes.\\
\bigskip

@@

\begin{figure}[!ht]
  \centering
  \includegraphics[width=\textwidth]{./figures/figure_1.png}
  \caption{\textbf{Overview of the solutions produced by the different network methods (Section~\ref{methods:methods}) on the GENESIS dataset.} As LEAN did not produce any significant solution (BH adjusted P\=/value~$<$~0.05), it is not shown. Unless indicated otherwise, results refer to SNPs for SConES GI, and to genes for the other methods. \textbf{(A)}~Overlap between the genes selected by each method, measured by Pearson correlation between indicator vectors (Sections~\ref{methods:algorithm_comparison} and \ref{methods:snp2gene}). \textbf{(B)}~Distribution of VEGAS2 P-values of the genes in the PPIN not selected by any network method (12\,213), and of those selected by 1 (575), 2 (73), or 3 (20) methods. \textbf{(C)}~Solution networks produced by the different methods. \textbf{(D)}~Manhattan plots of SNPs/genes; in black, the method's solution. The red line indicates the Bonferroni threshold (2.54~\texttimes{}~10\textsuperscript{-7} for SNPs, 1.53~\texttimes{}~10\textsuperscript{-6} for genes).}
  \label{fig:solution_overview}
\end{figure}

@@

\begin{figure}[!ht]
  \centering
  \includegraphics[width=.9\linewidth]{./figures/figure_2.pdf}
  \caption{ \textbf{Consensus solution on GENESIS (Section~\ref{methods:methods}).} \textbf{(A)}~Manhattan plot of genes; in black, the ones in the consensus solution. The red line indicates the Bonferroni threshold (1.53~\texttimes{}~10\textsuperscript{-6} for genes). \textbf{(B)}~Consensus network. Each gene is represented by a pie chart, which shows the methods that selected it. We enlarged the two most central genes (\emph{COPS5} and \emph{OFD1}), the known breast cancer susceptibility genes, and the BCAC-significant genes (Section~\ref{methods:bcac}). \textbf{(C)}~The nodes are in the same disposition as in panel B, but we indicated every gene name. We colored in pink the names of known breast cancer susceptibility genes and BCAC-significant genes.}
  \label{fig:consensus}
\end{figure}

@@

\begin{figure}[!ht]
  \centering
  \includegraphics[width=.8\linewidth]{./figures/figure_3.pdf}
  \caption{\textbf{Comparison of network methods on GENESIS.} Each method was run 5 times on a random subset containing 80\% of the samples and tested on the remaining samples (Section~\ref{methods:benchmark}). As LEAN did not select any gene, we excluded it from panels A and B. \textbf{(A)}~Number of SNPs selected by each method and number of SNPs in the active set (i.e., the number of SNPs selected by the classifier, Section~\ref{methods:classifier}). Points are the average over the 5 runs; the error bars represent the standard error of the mean. A grey diagonal line with slope 1 is added for comparison, indicating the upper bound of the active set. For reference, the active set of the classifier using all the SNPs as input included, on average, 154\,117.4 SNPs. \textbf{(B)}~Pairwise Pearson correlations of the solutions produced by different methods. A Pearson correlation of 1 means the two solutions are the same. \textbf{(C)}~Runtime of the evaluated methods, by type of network used (PPIN or SNP). For gene-based methods, inverted triangles represent the runtime of the algorithm alone, and circles the total time, which includes the algorithm themselves and the additional 119\,980 seconds (1 day and 9.33 hours) that VEGAS2 took on average to compute the gene scores from SNP summary statistics. \textbf{(D)}~True positive rate and false positive rate of the methods, obtained using different parameter combinations (Section~\ref{results:parameters}). We used as true positives BCAC-significant SNPs (for SConES and $\chi^2$ + Bonferroni) and genes (for the remaining methods, Section~\ref{methods:bcac}). We used the whole dataset in this panel.}
  \label{fig:benchmark}
  \end{figure}

@@

\begin{figure}[!ht]
  \centering
  \includegraphics[width=.8\linewidth]{./figures/figure_4.pdf}
  \caption{\textbf{Drawbacks encountered when using network methods.} \textbf{(A)}~DmGWAS solution, with the genes colored according to the -log$_{10}$ of their P\=/value. \textbf{(B)}~Number of times a gene was selected by either dmGWAS, heinz, LEAN, or SigMod in 100 rewirings of the PPIN (Section~\ref{methods:pathway_enrichment}) and its betweenness. \textbf{(C)}~Betweenness and -log\textsubscript{10} of the VEGAS2 P\=/value in BCAC for each of the nodes in the PPIN. We highlighted the genes selected by each method and the ones selected by more than one (``Consensus''). We labeled the three most central genes that were picked by any method. \textbf{(D)}~Overlap between the solutions of SConES GS, GM, or GI. Barplots are colored based on whether the SNPs map to a gene or not (Section~\ref{methods:snp2gene}).}
  \label{fig:issues}
  \end{figure}

@@

\begin{figure}[!ht]
  \centering
  \includegraphics[width=.8\linewidth]{./figures/figure_5.pdf}
  \caption{ \textbf{Stable consensus solution on GENESIS (Section~\ref{results:stable-consensus})}. \textbf{(A)}~Manhattan plot of genes; in black, the ones in the stable consensus solution. The red line indicates the Bonferroni threshold (1.53~\texttimes{}~10\textsuperscript{-6} for genes). \textbf{(B)}~Stable consensus network. Each gene is represented by a pie chart, which shows the methods that selected it. We enlarged the most central gene (\emph{CUL3}), the known breast cancer susceptibility genes, and the BCAC-significant genes (Section~\ref{methods:bcac}). \textbf{(C)}~The nodes are in the same disposition as in panel B, but we indicated every gene name. We colored in pink the names of known breast cancer susceptibility genes and BCAC-significant genes.}
  \label{fig:stable-consensus}
  \end{figure}

@@

>>>>

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Boosting GWAS using biological networks: a study on susceptibility to familial breast cancer} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Héctor Climente-González\textsuperscript{1,2,3,4*}, 
Christine Lonjou\textsuperscript{1,2,3}, 
Fabienne Lesueur\textsuperscript{1,2,3},
GENESIS study group\textsuperscript{\textpilcrow},
Dominique Stoppa-Lyonnet\textsuperscript{5,6,7\textcurrency}, 
Nadine Andrieu\textsuperscript{1,2,3}, 
Chloé-Agathe Azencott\textsuperscript{3,1,2}
\\
\bigskip
\textbf{1} Institut Curie, PSL Research University, Paris, France;\\
\textbf{2} INSERM, U900, Paris, France;\\
\textbf{3} MINES ParisTech, PSL Research University, CBIO-Centre for Computational Biology, Paris, France;\\
\textbf{4} RIKEN Center for Advanced Intelligence Project (AIP), Tokyo, Japan; \\
\textbf{5} Service de Génétique, Institut Curie, Paris, France;\\
\textbf{6} INSERM, U830, Paris, France;\\
\textbf{7} Université Paris Descartes, Paris, France.\\
\bigskip

@@

\begin{figure}[!ht]
  \centering
  %\includegraphics[width=\textwidth]{./figures/figure_1.png}
  \caption{\textbf{Overview of the solutions produced by the different network methods (Section~\ref{methods:methods}) on the GENESIS dataset.} As LEAN did not produce any significant solution (BH adjusted P\=/value~$<$~0.05), it is not shown. Unless indicated otherwise, results refer to SNPs for SConES GI, and to genes for the other methods. \textbf{(A)}~Overlap between the genes selected by each method, measured by Pearson correlation between indicator vectors (Sections~\ref{methods:algorithm_comparison} and \ref{methods:snp2gene}). \textbf{(B)}~Distribution of VEGAS2 P-values of the genes in the PPIN not selected by any network method (12\,213), and of those selected by 1 (575), 2 (73), or 3 (20) methods. \textbf{(C)}~Solution networks produced by the different methods. \textbf{(D)}~Manhattan plots of SNPs/genes; in black, the method's solution. The red line indicates the Bonferroni threshold (2.54~\texttimes{}~10\textsuperscript{-7} for SNPs, 1.53~\texttimes{}~10\textsuperscript{-6} for genes).}
  \label{fig:solution_overview}
\end{figure}

@@

\begin{figure}[!ht]
  \centering
  %\includegraphics[width=.9\linewidth]{./figures/figure_2.pdf}
  \caption{ \textbf{Consensus solution on GENESIS (Section~\ref{methods:methods}).} \textbf{(A)}~Manhattan plot of genes; in black, the ones in the consensus solution. The red line indicates the Bonferroni threshold (1.53~\texttimes{}~10\textsuperscript{-6} for genes). \textbf{(B)}~Consensus network. Each gene is represented by a pie chart, which shows the methods that selected it. We enlarged the two most central genes (\emph{COPS5} and \emph{OFD1}), the known breast cancer susceptibility genes, and the BCAC-significant genes (Section~\ref{methods:bcac}). \textbf{(C)}~The nodes are in the same disposition as in panel B, but we indicated every gene name. We colored in pink the names of known breast cancer susceptibility genes and BCAC-significant genes.}
  \label{fig:consensus}
\end{figure}

@@

\begin{figure}[!ht]
  \centering
  %\includegraphics[width=.8\linewidth]{./figures/figure_3.pdf}
  \caption{\textbf{Comparison of network methods on GENESIS.} Each method was run 5 times on a random subset containing 80\% of the samples and tested on the remaining samples (Section~\ref{methods:benchmark}). As LEAN did not select any gene, we excluded it from panels A and B. \textbf{(A)}~Number of SNPs selected by each method and number of SNPs in the active set (i.e., the number of SNPs selected by the classifier, Section~\ref{methods:classifier}). Points are the average over the 5 runs; the error bars represent the standard error of the mean. A grey diagonal line with slope 1 is added for comparison, indicating the upper bound of the active set. For reference, the active set of the classifier using all the SNPs as input included, on average, 154\,117.4 SNPs. \textbf{(B)}~Pairwise Pearson correlations of the solutions produced by different methods. A Pearson correlation of 1 means the two solutions are the same. \textbf{(C)}~Runtime of the evaluated methods, by type of network used (PPIN or SNP). For gene-based methods, inverted triangles represent the runtime of the algorithm alone, and circles the total time, which includes the algorithm themselves and the additional 119\,980 seconds (1 day and 9.33 hours) that VEGAS2 took on average to compute the gene scores from SNP summary statistics. \textbf{(D)}~True positive rate and false positive rate of the methods, obtained using different parameter combinations (Section~\ref{results:parameters}). We used as true positives BCAC-significant SNPs (for SConES and $\chi^2$ + Bonferroni) and genes (for the remaining methods, Section~\ref{methods:bcac}). We used the whole dataset in this panel.}
  \label{fig:benchmark}
  \end{figure}

@@

\begin{figure}[!ht]
  \centering
  %\includegraphics[width=.8\linewidth]{./figures/figure_4.pdf}
  \caption{\textbf{Drawbacks encountered when using network methods.} \textbf{(A)}~DmGWAS solution, with the genes colored according to the -log$_{10}$ of their P\=/value. \textbf{(B)}~Number of times a gene was selected by either dmGWAS, heinz, LEAN, or SigMod in 100 rewirings of the PPIN (Section~\ref{methods:pathway_enrichment}) and its betweenness. \textbf{(C)}~Betweenness and -log\textsubscript{10} of the VEGAS2 P\=/value in BCAC for each of the nodes in the PPIN. We highlighted the genes selected by each method and the ones selected by more than one (``Consensus''). We labeled the three most central genes that were picked by any method. \textbf{(D)}~Overlap between the solutions of SConES GS, GM, or GI. Barplots are colored based on whether the SNPs map to a gene or not (Section~\ref{methods:snp2gene}).}
  \label{fig:issues}
  \end{figure}

@@

\begin{figure}[!ht]
  \centering
  %\includegraphics[width=.8\linewidth]{./figures/figure_5.pdf}
  \caption{ \textbf{Stable consensus solution on GENESIS (Section~\ref{results:stable-consensus})}. \textbf{(A)}~Manhattan plot of genes; in black, the ones in the stable consensus solution. The red line indicates the Bonferroni threshold (1.53~\texttimes{}~10\textsuperscript{-6} for genes). \textbf{(B)}~Stable consensus network. Each gene is represented by a pie chart, which shows the methods that selected it. We enlarged the most central gene (\emph{CUL3}), the known breast cancer susceptibility genes, and the BCAC-significant genes (Section~\ref{methods:bcac}). \textbf{(C)}~The nodes are in the same disposition as in panel B, but we indicated every gene name. We colored in pink the names of known breast cancer susceptibility genes and BCAC-significant genes.}
  \label{fig:stable-consensus}
  \end{figure}

@@

We wish to thank Om Kulkarni for helpful discussion on gene-based GWAS and PPIN databases, Vivien Goepp for his constructive comments of the manuscript, and the genetic epidemiology platform (the PIGE, Plateforme d'Investigation en Génétique et Epidemiologie: S. Eon-Marchais, M. Marcou, D. Le Gal, L. Toulemonde, J. Beauvallet, N. Mebirouk, E. Cavaciuti), the biological resource center (S. Mazoyer, F. Damiola, L. Barjhoux, C. Verny-Pierre, V. Sornin).

% \bibliography{bibliography.bib} 
\begin{thebibliography}{10}

  \bibitem{bush_chapter_2012}
  Bush WS, Moore JH.
  \newblock Chapter 11: {Genome}-{Wide} {Association} {Studies}.
  \newblock PLoS Computational Biology. 2012;8(12):e1002822.
  \newblock doi:{10.1371/journal.pcbi.1002822}.

  \bibitem{buniello_nhgri-ebi_2019}
  Buniello A, MacArthur JA, Cerezo M, Harris LW, Hayhurst J, Malangone C, et~al.
  \newblock The {NHGRI}-{EBI} {GWAS} {Catalog} of published genome-wide
    association studies, targeted arrays and summary statistics 2019.
  \newblock Nucleic Acids Research. 2019;47(D1):D1005--D1012.
  \newblock doi:{10.1093/nar/gky1120}.

  \bibitem{visscher_10_2017}
  Visscher PM, Wray NR, Zhang Q, Sklar P, McCarthy MI, Brown MA, et~al.
  \newblock 10 {Years} of {GWAS} {Discovery}: {Biology}, {Function}, and
    {Translation}.
  \newblock The American Journal of Human Genetics. 2017;101(1):5--22.
  \newblock doi:{10.1016/j.ajhg.2017.06.005}.

  \bibitem{wang_statistical_2018}
  Wang MH, Cordell HJ, Van~Steen K.
  \newblock Statistical methods for genome-wide association studies.
  \newblock Seminars in Cancer Biology.
    2018;doi:{10.1016/j.semcancer.2018.04.008}.

  \bibitem{barton_infinitesimal_2017}
  Barton NH, Etheridge AM, Véber A.
  \newblock The infinitesimal model: {Definition}, derivation, and implications.
  \newblock Theoretical Population Biology. 2017;118:50--73.
  \newblock doi:{10.1016/j.tpb.2017.06.001}.

  \bibitem{boyle_expanded_2017}
  Boyle EA, Li YI, Pritchard JK.
  \newblock An {Expanded} {View} of {Complex} {Traits}: {From} {Polygenic} to
    {Omnigenic}.
  \newblock Cell. 2017;169(7):1177--1186.
  \newblock doi:{10.1016/j.cell.2017.05.038}.

  \bibitem{furlong_human_2013}
  Furlong LI.
  \newblock Human diseases through the lens of network biology.
  \newblock Trends in Genetics. 2013;29(3):150--159.
  \newblock doi:{10.1016/j.tig.2012.11.004}.

  \bibitem{leisersonNetworkAnalysisGWAS2013}
  Leiserson MD, {Eldridge, Jonathan V}, {Ramachandran, Sohini}, {Raphael,
    Benjamin J}.
  \newblock Network analysis of {GWAS} data.
  \newblock Current Opinion in Genetics \& Development. 2013;23(6):602--610.

  \bibitem{barabasi_network_2011}
  Barabási AL, Gulbahce N, Loscalzo J.
  \newblock Network medicine: a network-based approach to human disease.
  \newblock Nature Reviews Genetics. 2011;12(1):56--68.
  \newblock doi:{10.1038/nrg2918}.

  \bibitem{cai_broker_2010}
  Cai JJ, Borenstein E, Petrov DA.
  \newblock Broker {Genes} in {Human} {Disease}.
  \newblock Genome Biology and Evolution. 2010;2:815--825.
  \newblock doi:{10.1093/gbe/evq064}.

  \bibitem{azencott_network-guided_2016}
  Azencott CA.
  \newblock Network-{Guided} {Biomarker} {Discovery}.
  \newblock In: Machine {Learning} for {Health} {Informatics}. vol. 9605. Cham:
    Springer International Publishing; 2016. p. 319--336.
  \newblock Available from:
    \url{http://link.springer.com/10.1007/978-3-319-50478-0_16}.

  \bibitem{huang_systematic_2018}
  Huang JK, Carlin DE, Yu MK, Zhang W, Kreisberg JF, Tamayo P, et~al.
  \newblock Systematic {Evaluation} of {Molecular} {Networks} for {Discovery} of
    {Disease} {Genes}.
  \newblock Cell Systems. 2018;6(4):484--495.e5.
  \newblock doi:{10.1016/j.cels.2018.03.001}.

  \bibitem{gwinner_network-based_2016}
  Gwinner F, Boulday G, Vandiedonck C, Arnould M, Cardoso C, Nikolayeva I, et~al.
  \newblock Network-based analysis of omics data: {The} {LEAN} method.
  \newblock Bioinformatics. 2016; p. btw676.
  \newblock doi:{10.1093/bioinformatics/btw676}.

  \bibitem{jia_dmgwas:_2011}
  Jia P, Zheng S, Long J, Zheng W, Zhao Z.
  \newblock {dmGWAS}: dense module searching for genome-wide association studies
    in protein–protein interaction networks.
  \newblock Bioinformatics. 2011;27(1):95--102.
  \newblock doi:{10.1093/bioinformatics/btq615}.

  \bibitem{dittrich_identifying_2008}
  Dittrich MT, Klau GW, Rosenwald A, Dandekar T, Muller T.
  \newblock Identifying functional modules in protein-protein interaction
    networks: an integrated exact approach.
  \newblock Bioinformatics. 2008;24(13):i223--i231.
  \newblock doi:{10.1093/bioinformatics/btn161}.

  \bibitem{leiserson_pan-cancer_2015}
  Leiserson MDM, Vandin F, Wu HT, Dobson JR, Eldridge JV, Thomas JL, et~al.
  \newblock Pan-cancer network analysis identifies combinations of rare somatic
    mutations across pathways and protein complexes.
  \newblock Nature Genetics. 2015;47(2):106--114.
  \newblock doi:{10.1038/ng.3168}.

  \bibitem{azencott_efficient_2013}
  Azencott CA, Grimm D, Sugiyama M, Kawahara Y, Borgwardt KM.
  \newblock Efficient network-guided multi-locus association mapping with graph
    cuts.
  \newblock Bioinformatics. 2013;29(13):i171--i179.
  \newblock doi:{10.1093/bioinformatics/btt238}.

  \bibitem{liu_sigmod:_2017}
  Liu Y, Brossard M, Roqueiro D, Margaritte-Jeannin P, Sarnowski C, Bouzigon E,
    et~al.
  \newblock {SigMod}: an exact and efficient method to identify a strongly
    interconnected disease-associated module in a gene network.
  \newblock Bioinformatics. 2017; p. btx004.
  \newblock doi:{10.1093/bioinformatics/btx004}.

  \bibitem{sinilnikova_genesis:_2016}
  Sinilnikova OM, Dondon MG, Eon-Marchais S, Damiola F, Barjhoux L, Marcou M,
    et~al.
  \newblock {GENESIS}: a {French} national resource to study the missing
    heritability of breast cancer.
  \newblock BMC Cancer. 2016;16(1):13.
  \newblock doi:{10.1186/s12885-015-2028-9}.

  \bibitem{sakoda_turning_2013}
  Sakoda LC, Jorgenson E, Witte JS.
  \newblock Turning of {COGS} moves forward findings for hormonally mediated
    cancers.
  \newblock Nature Genetics. 2013;45(4):345--348.
  \newblock doi:{10.1038/ng.2587}.

  \bibitem{chang_second-generation_2015}
  Chang CC, Chow CC, Tellier LC, Vattikuti S, Purcell SM, Lee JJ.
  \newblock Second-generation {PLINK}: rising to the challenge of larger and
    richer datasets.
  \newblock GigaScience. 2015;4(1):7.
  \newblock doi:{10.1186/s13742-015-0047-8}.

  \bibitem{mishra_vegas2:_2015}
  Mishra A, Macgregor S.
  \newblock {VEGAS}2: {Software} for {More} {Flexible} {Gene}-{Based} {Testing}.
  \newblock Twin Research and Human Genetics. 2015;18(1):86--91.
  \newblock doi:{10.1017/thg.2014.79}.

  \bibitem{frankish_gencode_2019}
  Frankish A, Diekhans M, Ferreira AM, Johnson R, Jungreis I, Loveland J, et~al.
  \newblock {GENCODE} reference annotation for the human and mouse genomes.
  \newblock Nucleic Acids Research. 2019;47(D1):D766--D773.
  \newblock doi:{10.1093/nar/gky955}.

  \bibitem{das_hint:_2012}
  Das J, Yu H.
  \newblock {HINT}: {High}-quality protein interactomes and their applications in
    understanding human disease.
  \newblock BMC Systems Biology. 2012;6(1):92.
  \newblock doi:{10.1186/1752-0509-6-92}.

  \bibitem{dmgwas}
  Wang Q, Jia P. dmGWAS 3.0; 2014.
  \newblock \url{https://bioinfo.uth.edu/dmGWAS/}.

  \bibitem{ljubic_algorithmic_2006}
  Ljubić I, Weiskircher R, Pferschy U, Klau GW, Mutzel P, Fischetti M.
  \newblock An {Algorithmic} {Framework} for the {Exact} {Solution} of the
    {Prize}-{Collecting} {Steiner} {Tree} {Problem}.
  \newblock Mathematical Programming. 2006;105(2-3):427--449.
  \newblock doi:{10.1007/s10107-005-0660-x}.

  \bibitem{beisser_bionet:_2010}
  Beisser D, Klau GW, Dandekar T, Muller T, Dittrich MT.
  \newblock {BioNet}: an {R}-{Package} for the functional analysis of biological
    networks.
  \newblock Bioinformatics. 2010;26(8):1129--1130.
  \newblock doi:{10.1093/bioinformatics/btq089}.

  \bibitem{heinz}
  Dittrich M, Beisser D. BioNet; 2008.
  \newblock \url{https://bioconductor.org/packages/BioNet/}.

  \bibitem{nakka_gene_2016}
  Nakka P, Raphael BJ, Ramachandran S.
  \newblock Gene and {Network} {Analysis} of {Common} {Variants} {Reveals}
    {Novel} {Associations} in {Multiple} {Complex} {Diseases}.
  \newblock Genetics. 2016;204(2):783--798.
  \newblock doi:{10.1534/genetics.116.188391}.

  \bibitem{scheid_twilight;_2005}
  Scheid S, Spang R.
  \newblock twilight; a {Bioconductor} package for estimating the local false
    discovery rate.
  \newblock Bioinformatics. 2005;21(12):2921--2922.
  \newblock doi:{10.1093/bioinformatics/bti436}.

  \bibitem{hotnet2}
  Leiserson MDM, Vandin F, Wu HT, Dobson JR, Eldridge JV, Thomas JL, et~al..
    HotNet2; 2018.
  \newblock \url{https://github.com/raphael-group/hotnet2}.

  \bibitem{leanr}
  Gwinner F. LEANR; 2016.
  \newblock \url{https://cran.r-project.org/web/packages/LEANR/}.

  \bibitem{martini}
  Climente-González H, Azencott CA. martini; 2019.
  \newblock \url{https://www.bioconductor.org/packages/martini/}.

  \bibitem{climente-gonzalezMartiniPackageGenomewide2021}
  Climente-González H, Azencott CA.
  \newblock martini: an {R} package for genome-wide association studies using
    {SNP} networks.
  \newblock Bioinformatics; 2021.
  \newblock Available from:
    \url{http://biorxiv.org/lookup/doi/10.1101/2021.01.25.428047}.

  \bibitem{sigmod}
  Liu Y. SigMod v2; 2018.
  \newblock \url{https://github.com/YuanlongLiu/SigMod}.

  \bibitem{Jassal2019}
  Jassal B, Matthews L, Viteri G, Gong C, Lorente P, Fabregat A, et~al.
  \newblock The reactome pathway knowledgebase.
  \newblock Nucleic Acids Research. 2019;doi:{10.1093/nar/gkz1031}.

  \bibitem{Yu2016}
  Yu G, He QY.
  \newblock {ReactomePA}: an R/Bioconductor package for reactome pathway analysis
    and visualization.
  \newblock Molecular {BioSystems}. 2016;12(2):477--479.
  \newblock doi:{10.1039/c5mb00663e}.

  \bibitem{Benjamini1995}
  Benjamini Y, Hochberg Y.
  \newblock Controlling the False Discovery Rate: A Practical and Powerful
    Approach to Multiple Testing.
  \newblock Journal of the Royal Statistical Society: Series B (Methodological).
    1995;57(1):289--300.
  \newblock doi:{10.1111/j.2517-6161.1995.tb02031.x}.

  \bibitem{nogueira_measuring_2016}
  Nogueira S, Brown G.
  \newblock Measuring the {Stability} of {Feature} {Selection}.
  \newblock In: Machine {Learning} and {Knowledge} {Discovery} in {Databases}.
    vol. 9852. Cham: Springer International Publishing; 2016. p. 442--457.
  \newblock Available from:
    \url{http://link.springer.com/10.1007/978-3-319-46227-1_28}.

  \bibitem{Metcalfe2008}
  Metcalfe KA, Finch A, Poll A, Horsman D, Kim-Sing C, Scott J, et~al.
  \newblock Breast cancer risks in women with a family history of breast or
    ovarian cancer who have tested negative for a {BRCA}1 or {BRCA}2 mutation.
  \newblock British Journal of Cancer. 2008;100(2):421--425.
  \newblock doi:{10.1038/sj.bjc.6604830}.

  \bibitem{pinero_disgenet:_2017}
  Piñero J, Bravo A, Queralt-Rosinach N, Gutiérrez-Sacristán A, Deu-Pons J,
    Centeno E, et~al.
  \newblock {DisGeNET}: a comprehensive platform integrating information on human
    disease-associated genes and variants.
  \newblock Nucleic Acids Research. 2017;45(D1):D833--D839.
  \newblock doi:{10.1093/nar/gkw943}.

  \bibitem{Michailidou2017}
  Michailidou K, Lindstr\"{o}m S, Dennis J, Beesley J, Hui S, Kar S, et~al.
  \newblock Association analysis identifies 65 new breast cancer risk loci.
  \newblock Nature. 2017;551(7678):92--94.
  \newblock doi:{10.1038/nature24284}.

  \bibitem{the_1000_genomes_project_consortium_global_2015}
  {The 1000 Genomes Project Consortium}, Gibbs RA, Boerwinkle E, Doddapaneni H,
    Han Y, Korchina V, et~al.
  \newblock A global reference for human genetic variation.
  \newblock Nature. 2015;526(7571):68--74.
  \newblock doi:{10.1038/nature15393}.

  \bibitem{Mulligan2011}
  Mulligan AM, , Couch FJ, Barrowdale D, Domchek SM, Eccles D, et~al.
  \newblock Common breast cancer susceptibility alleles are associated with
    tumour subtypes in {BRCA}1 and {BRCA}2 mutation carriers: results from the
    Consortium of Investigators of Modifiers of {BRCA}1/2.
  \newblock Breast Cancer Research. 2011;13(6).
  \newblock doi:{10.1186/bcr3052}.

  \bibitem{rinella_genetic_2013}
  Rinella ES, Shao Y, Yackowski L, Pramanik S, Oratz R, Schnabel F, et~al.
  \newblock Genetic variants associated with breast cancer risk for {Ashkenazi}
    {Jewish} women with strong family histories but no identifiable {BRCA}1/2
    mutation.
  \newblock Human Genetics. 2013;132(5):523--536.
  \newblock doi:{10.1007/s00439-013-1269-4}.

  \bibitem{brisbin_meta-analysis_2011}
  Brisbin AG, Asmann YW, Song H, Tsai YY, Aakre JA, Yang P, et~al.
  \newblock Meta-analysis of 8q24 for seven cancers reveals a locus between {NOV}
    and {ENPP}2 associated with cancer development.
  \newblock BMC Medical Genetics. 2011;12(1):156.
  \newblock doi:{10.1186/1471-2350-12-156}.

  \bibitem{search_newly_2009}
  {SEARCH}, {The GENICA Consortium}, {kConFab}, {Australian Ovarian Cancer Study
    Group}, Ahmed S, Thomas G, et~al.
  \newblock Newly discovered breast cancer susceptibility loci on 3p24 and
    17q23.2.
  \newblock Nature Genetics. 2009;41(5):585--590.
  \newblock doi:{10.1038/ng.354}.

  \bibitem{nielsen_hereditary_2016}
  Nielsen FC, van Overeem~Hansen T, Sørensen CS.
  \newblock Hereditary breast and ovarian cancer: new genes in confined pathways.
  \newblock Nature Reviews Cancer. 2016;16(9):599--612.
  \newblock doi:{10.1038/nrc.2016.72}.

  \bibitem{pinero_uncovering_2016}
  Piñero J, Berenstein A, Gonzalez-Perez A, Chernomoretz A, Furlong LI.
  \newblock Uncovering disease mechanisms through network biology in the era of
    {Next} {Generation} {Sequencing}.
  \newblock Scientific Reports. 2016;6(1):24570.
  \newblock doi:{10.1038/srep24570}.

  \bibitem{quigley_5p12_2014}
  Quigley DA, Fiorito E, Nord S, Van~Loo P, Alnaes GG, Fleischer T, et~al.
  \newblock The 5p12 breast cancer susceptibility locus affects {MRPS}30
    expression in estrogen-receptor positive tumors.
  \newblock Molecular Oncology. 2014;8(2):273--284.
  \newblock doi:{10.1016/j.molonc.2013.11.008}.

  \bibitem{Yu2016Repositioning}
  Yu M, Li R, Zhang J.
  \newblock Repositioning of antibiotic levofloxacin as a mitochondrial
    biogenesis inhibitor to target breast cancer.
  \newblock Biochemical and Biophysical Research Communications.
    2016;471(4):639--645.
  \newblock doi:{10.1016/j.bbrc.2016.02.072}.

  \bibitem{liu_jab1_cops5_2018}
  Liu G, Claret FX, Zhou F, Pan Y.
  \newblock Jab1/{COPS}5 as a {Novel} {Biomarker} for {Diagnosis}, {Prognosis},
    {Therapy} {Prediction} and {Therapeutic} {Tools} for {Human} {Cancer}.
  \newblock Frontiers in Pharmacology. 2018;9:135.
  \newblock doi:{10.3389/fphar.2018.00135}.

  \bibitem{deloscamposComplexTraitPredictionEra2018}
  de~los Campos G, Vazquez AI, Hsu S, Lello L.
  \newblock Complex-{Trait} {Prediction} in the {Era} of {Big} {Data}.
  \newblock Trends in Genetics. 2018;34(10):746--754.
  \newblock doi:{10.1016/j.tig.2018.07.004}.

  \bibitem{nikolayeva_network_2018}
  Nikolayeva I, Guitart~Pla O, Schwikowski B.
  \newblock Network module identification—{A} widespread theoretical bias and
    best practices.
  \newblock Methods. 2018;132:19--25.
  \newblock doi:{10.1016/j.ymeth.2017.08.008}.

  \bibitem{Ioachim2002}
  Ioachim E, Charchanti A, Briasoulis E, Karavasilis V, Tsanou H, Arvanitis DL,
    et~al.
  \newblock Immunohistochemical expression of extracellular matrix components
    tenascin, fibronectin, collagen type {IV} and laminin in breast cancer: their
    prognostic value and role in tumour invasion and progression.
  \newblock European Journal of Cancer. 2002;38(18):2362--2370.
  \newblock doi:{10.1016/s0959-8049(02)00210-1}.

  \bibitem{Yi2016}
  Yi W, Xiao E, Ding R, Luo P, Yang Y.
  \newblock High expression of fibronectin is associated with poor prognosis,
    cell proliferation and malignancy via the {NF}-$\kappa$B/p53-apoptosis
    signaling pathway in colorectal cancer.
  \newblock Oncology Reports. 2016;36(6):3145--3153.
  \newblock doi:{10.3892/or.2016.5177}.

  \bibitem{Sponziello2016}
  Sponziello M, Rosignolo F, Celano M, Maggisano V, Pecce V, Rose RFD, et~al.
  \newblock Fibronectin-1 expression is increased in aggressive thyroid cancer
    and favors the migration and invasion of cancer cells.
  \newblock Molecular and Cellular Endocrinology. 2016;431:123--132.
  \newblock doi:{10.1016/j.mce.2016.05.007}.

  \bibitem{ahmed_newly_2009}
  Ahmed S, Thomas G, Ghoussaini M, Healey CS, Humphreys MK, Platte R, et~al.
  \newblock Newly discovered breast cancer susceptibility loci on 3p24 and
    17q23.2.
  \newblock Nature Genetics. 2009;41(5):585--590.
  \newblock doi:{10.1038/ng.354}.

  \bibitem{breyer_expressed_2014}
  Breyer J, Dorset D, Clark T, Bradley K, Wahlfors T, McReynolds K, et~al.
  \newblock An {Expressed} {Retrogene} of the {Master} {Embryonic} {Stem} {Cell}
    {Gene} {POU}5F1 {Is} {Associated} with {Prostate} {Cancer} {Susceptibility}.
  \newblock The American Journal of Human Genetics. 2014;94(3):395--404.
  \newblock doi:{10.1016/j.ajhg.2014.01.019}.

  \bibitem{Chen2016}
  Chen HY, Chen RH.
  \newblock Cullin 3 Ubiquitin Ligases in Cancer Biology: Functions and
    Therapeutic Implications.
  \newblock Frontiers in Oncology. 2016;6.
  \newblock doi:{10.3389/fonc.2016.00113}.

  \bibitem{Loignon2009}
  Loignon M, Miao W, Hu L, Bier A, Bismar TA, Scrivens PJ, et~al.
  \newblock Cul3 overexpression depletes Nrf2 in breast cancer and is associated
    with sensitivity to carcinogens, to oxidative stress, and to chemotherapy.
  \newblock Molecular Cancer Therapeutics. 2009;8(8):2432--2440.
  \newblock doi:{10.1158/1535-7163.mct-08-1186}.
